Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
Checked the last change.

\textbf{Clone Detection Configuration: }
We are aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
In total, we have four configurations: Simian with the default
configuration ($S_D$), Simian with EvaClone configuration ($S_E$), 
NiCad with the default configurations ($N_D$)
and NiCad with EvaClone configuration ($N_E$).

@@

For manual investigation, the first author, who has been working on clone detection research for 
two years, took the role of the main investigator performing a manual 
validation and classification of the filtered clone pairs. 
%By consulting the cloning patterns, 
The main investigator went through each clone pair candidate, 
looked at the clones, and decided if they are a true positive or a
false positive and classified them into an appropriate pattern. 
%the most appropriate cloning pattern for the pair. 
To mitigate the human error of the manual investigation, 
the second author took the role of the validating investigator, performing a
validation on 10\% (364 pairs) of the clone pairs judged by the main
investigator. After the validation, the results from the two
investigators were compared and 61 conflicts were discussed and resolved.
There were 3 conflicts that the two investigators could not find a consensus 
and the third author was involved for the final judgement.

@@

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
any pairs with evidence of cloning from Stack Overflow to Qualitas
projects. This is very likely due to the age of the Qualitas corpus.
However, with a newer data set, one can find online clones in
this direction as shown in another study~\cite{An2017}.

@@

%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals. 
Our study discovers links from code in open source projects to code snippets on Stack Overflow using clone detection techniques. These links enable us to discover outdate code and licensing problems. The links can be exploited further to mitigate the problems of reusing outdated online clones and incompatible license on Stack Overflow code snippets. We propose the following actionable items:

@@

\textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed. The system can leverage the online clone detection techniques in this study to periodically check if the cloned snippets are still up-to-date with their originals. %Moreover, Stack Overflow posters have to provide the information of the project including the original file name and its online repository (if exists). 
With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly. On the other hand, with a crowdsourcing solution using an IDE plug-in, developers can also report the corrected version of outdated code back to the original Stack Overflow threads when they reuse outdated code and makes corrections to them.

@@

\textbf{Internal validity:} 
%
We could not verify all the 315,786,118 clone pairs reported by the
clone detection tools in this study.  Nevertheless, we applied
different mechanisms to ensure the validity to the subset of clone
pairs we classified.  First, we used two widely-used
clone detection tools, Simian and NiCad.  We tried three other
clone detectors but could not add them to the study due to their
scalability issues and susceptibility to incomplete code snippets.
Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
to prioritise and filters clone pairs for the manual
classification. The agreed clone pairs that passed \textit{good}- and
\textit{ok}- criteria had a higher chance to be true positive. 
Nevertheless, we might still suffers from false negatives, i.e.~online 
code clones that are not reported by the tools or filtered 
out by the automatic classifier before the manual investigation.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

@@

\FIXME{This needs rewriting}

>>>>

\textbf{Clone Detection Configuration: }
We are aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
In total, we have four configurations: Simian with the default
configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
NiCad with the default configuration ($N_D$)
and NiCad with the EvaClone configuration ($N_E$).

@@

For manual investigation, the first author, who has been working on clone detection research for 
two years, took the role of the main investigator performing a manual 
validation and classification of the filtered clone pairs. 
%By consulting the cloning patterns, 
The main investigator went through each clone pair candidate, 
looked at the clones, and decided if they are a true positive or a
false positive and classified them into an appropriate pattern. 
%the most appropriate cloning pattern for the pair. 
To mitigate the human error of the manual investigation, 
the second author took the role of the validating investigator, performing a
validation on 10\% (364 pairs) of the clone pairs judged by the main
investigator. After the validation, the results from the two
investigators were compared and 61 conflicts were discussed and resolved.
There were 3 conflicts where the two investigators could not find a consensus 
and the third author was involved for the final judgement.

@@

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
any pairs with evidence of cloning from Stack Overflow to Qualitas
projects. This is very likely due to the age of the Qualitas corpus as
another study~\cite{An2017} showed the presence of clones from Stack
Overflow in newer open source data sets.

@@

%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals. 
Our study discovers links from code in open source projects to code
snippets on Stack Overflow using clone detection techniques. These
links enable us to discover outdated code and licensing problems. The
links can be exploited further to mitigate the problems of reusing
outdated online clones and incompatible license on Stack Overflow code
snippets. We propose the following actionable items:

@@

\textbf{Detective measure:} A system to detect outdated source code
snippets on Stack Overflow is needed. The system can leverage the
online clone detection techniques in this study to periodically check
if the cloned snippets are still up-to-date with their
originals. %Moreover, Stack Overflow posters have to provide the information of the project including the original file name and its online repository (if exists).
With such a system, the poster can be notified when the code has been
updated in the original project so that he/she can update their code
on Stack Overflow accordingly. On the other hand, with a crowdsourcing
solution using an IDE plug-in, developers can also report the
corrected version of outdated code back to the original Stack Overflow
threads when they reuse outdated code and make corrections to them.

@@

\textbf{Internal validity:} 
%
We could not verify all the 315,786,118 clone pairs reported by the
clone detection tools in this study.  Nevertheless, we applied
different mechanisms to ensure the validity to the subset of clone
pairs we classified.  First, we used two widely-used
clone detection tools, Simian and NiCad.  We tried three other
clone detectors but could not add them to the study due to their
scalability issues and susceptibility to incomplete code snippets.
Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
to prioritise and filters clone pairs for the manual
classification. The agreed clone pairs that passed \textit{good}- and
\textit{ok}- criteria had a higher chance to be true positive. 
Nevertheless, we might still suffers from false negatives, i.e.~online 
code clones that are not reported by the tools or are filtered 
out by the automatic classifier before the manual investigation.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

@@
